The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
EOD
Aim for 'Molecular Phylogenetics and Evolution'

  % One or two sentences providing a basic
  % introduction to the field,
  % comprehensible to a scientist in any discipline.

@@

{\bf Keywords:} computational biology, evolution, phylogenetics, Bayesian analysis, tree prior
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\richel{Have you already looked up for a target journal?} 
\gio{Honestly I have literally no idea how to select a good journal for this kind of article.}
\richel{
  May I suggest we aim for Molecular Phylogenetics and Evolution, the same journal as the raket paper?
}

>>>>

  % One or two sentences providing a basic
  % introduction to the field,
  % comprehensible to a scientist in any discipline.
  Phylogenetics is the field in which phylogenies are
  created from DNA, RNA or protein alignments.
  The evolutionary relationships between species or
  individuals

@@

{\bf Keywords:} computational biology, evolution, phylogenetics, Bayesian analysis, tree prior
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
